---
title: "The fars package"
author: "Andrew G."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(fars)
library(knitr)
```

The fars package provides several tools for interacting with data sets from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, a nationwide collection of information about deaths in traffic accidents in the United States.

A fars data set can be read directly by name using the ${\tt fars\_read}$ function. For instance, if the file accident_2013.csv.bz2 exists in the working directory, then ${\tt fars\_read("accident\_2013.csv.bz2")}$ will load it into R's working memory.

A group of fars data sets can be read in by specifying their years in the ${\tt fars\_read\_years}$ function. For instance,

```{r warning=FALSE}
years <- 2013:2015
fars_list <- fars_read_years(years)
```

Summary data about fars sets can be obtained with the ${\tt fars\_summarize\_years}$.

```{r}
fars_summary <- fars_summarize_years(years)
kable(fars_summary)
```

Finally, the ${\tt fars\_map\_state}$ function plots rudimentary state-level maps of traffic fatalities based on the state's numerical id number. For instance, here's a map of traffic fatalities in Alabama in 2014.

```{r}
fars_map_state(1, 2014)
```
